ms_0_intro

### 2017-08-17 man/ms_0_intro.Rmd
add aims of study

>>>>

* The vegetation response to water deficit was assessed using remote sensing information and dendrocronologial data.

:red_circle: Algo de las sequías

## Aims
`$IMPROVE$`

In this study we combined remote sensing information and dendroecological methods to evaluate the drought impacts in both greenees and growth of *Q. pyrenaica* forests in Sierra Nevada. Specifically,

The aims of this work were:

* To evaluate how extreme drought events affected the greennes and growth of *Q. pyreancia* forests in ther rear edge,

* to analyze the resilience of these forests to sucessive extrme drought events, 
* and to explore differences in the resilience metrics between populations located in contrasting slopes within the rear edge of the distribution of this species.
